Hydra battles in Coq

### 2020-08-31 latex/hydras.tex
table of notations

\section{Index}
\subsection{Infix notations}

\begin{tabular}{|c|c|c|c|l|}
\hline
Name & Ascii&Math& Description& Where \\\hline
 \texttt{on\_lt} & \texttt{alpha o< beta}&$\alpha<\beta$& ordinal inequality & \vref{sect:on-lt-notation}\\
 \texttt{on\_le} & \texttt{alpha o<= beta}&$\alpha\leq\beta$& ordinal inequality & \vref{sect:on-lt-notation}\\
\texttt{oplus} & \texttt{alpha o+ beta} & $\alpha \oplus \beta$ & Hessenberg sum & \vref{sect:infix-oplus} \\
\texttt{round} & \texttt{h -1-> h'} & & round of a battle & \vref{sect:infix-round} \\
\hline
\end{tabular}

>>>>

\section{Index}
Some notations may belong to several scopes. For instance, ``\texttt{o<}'' is
bound in \texttt{ON\_scope}, \texttt{E0\_scope}, \texttt{t1\_scope}, etc., and locally in several libraries.

\subsection{Infix notations}

\vspace{4pt}

\begin{tabular}{|c|c|c|c|l|}
\hline
Name & Ascii&Math& Description& Page \\\hline
 \texttt{on\_lt} & \texttt{alpha o< beta}&$\alpha<\beta$& ordinal inequality & \pageref{sect:on-lt-notation}\\
 \texttt{on\_le} & \texttt{alpha o<= beta}&$\alpha\leq\beta$& ordinal inequality & \pageref{sect:on-lt-notation}\\
\texttt{plus} & \texttt{alpha + beta} & $\alpha + \beta$ & Ordinal addition & \pageref{sect:infix-oplus} \\
\texttt{oplus} & \texttt{alpha o+ beta} & $\alpha \oplus \beta$ & Hessenberg sum & \pageref{sect:infix-oplus} \\
\texttt{round} & \texttt{h -1-> h'} & & one round of a battle & \pageref{sect:infix-round} \\
\texttt{rounds} & \texttt{h -+-> h'} & & one or more  rounds of a battle & \pageref{sect:infix-rounds} \\
\texttt{round\_star} & \texttt{h -*-> h'} & & any number of rounds of a battle & \pageref{sect:infix-rounds} \\

\hline
\end{tabular}

\subsection{Other notations}

\begin{tabular}{|c|c|c|c|l|}
\hline
Name & Ascii&Math& Description& Page \\\hline
omega & \texttt{omega} & $\omega$ &   the first infinite ordinal   & \pageref{sect:notation-omega},\dots\\
phi0     & \texttt{phi0 alpha} & $\varphi_0(\alpha),\; \omega^\alpha$&exponential of base $\omega$ & \pageref{sect:notation-phi0}\\

\hline
\end{tabular}
